A multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-05-24 manuscript/manuscript.tex
references

>>>>

\begin{thebibliography}{}

\bibitem{ } Franczak BC, Tortora C, Browne RP, McNicholas PD. Unsupervised learning via mixtures of skewed distributions with hypercube contours. \textit{Pattern Recognition Letters}. 2015 Jun 1;58:69-76.

\bibitem{ } Ganjali M, Baghfalaki T. A Bayesian shared parameter model for analysing longitudinal skewed responses with nonignorable dropout. \textit{International Journal of Statistics in Medical Research}. 2014 Apr 1;3(2):103.

\bibitem{ } Cox, D. R. (1972). Regression models and life tables (with
discussion).  \textit{Journal of the Royal Statistical Society, Series B}
\textbf{34,} 187--200.

\bibitem{ }  Hastie, T., Tibshirani, R., and Friedman, J. (2001). \textit{The 
Elements of Statistical Learning: Data Mining, Inference, and Prediction}.
New York: Springer.

\end{thebibliography}
